PMC Survey QC Analysis

### 2021-08-18 QC analysis.Rmd
fix qc
start comparision

  ## Intro
  Here we are performing an analysis of 200 articles which is randomly selected from 1500 PMC articles.

@@

>>>>

## Intro

Here we are performing an analysis of 200 articles which is randomly selected from 1500 PMC articles.

@@

## Cross check

```{R,crosscheck}
y <- read.table("PMC_2019-analysis.tsv",header=TRUE,fill=TRUE,sep="\t")
myqc<-x[1,,drop=TRUE]
head(myqc)
mypmc<-myqc[[1]]
str(myqc)

ydat<-y[which(y$Pubmed.Central.ID==mypmc),,drop=TRUE]
str(ydat)
